Unifying Lower Bounds on Prediction Dimension of Consistent Convex Surrogates

### 2021-01-29 colt-21/cvx-flats.tex
Proof of Cor 28

If given, we use $\ell: \R \times \Y \to \reals$ to denote a \emph{target loss}, with predictions $r\in\R$.
%where the goal is minimize expected loss, $\E ~ \ell(f(X),Y)$ for pairs $X,Y$ drawn from some distribution.
Similarly, $L: \reals^d \times \Y \to \reals$ will typically denote a \emph{surrogate} loss, with surrogate predictions $u \in \reals^d$.
We write $\L_d $ for the set of $\mathcal{B}(\reals^d) \otimes \Y$-measurable and lower semi-continuous surrogates $L : \reals^d \times\Y \to \reals$ such that $\E_{Y \sim p} L(u,Y) < \infty$ for all $u \in \reals^d, p \in \P$, that are minimizable in that $\argmin_{u} \exploss{L}{u}{p}$ is nonempty for all $p\in\P$.
Moreover, $\Lcvx_d \subseteq \L_d$ is the set of convex (in $\reals^d$ for every $y \in \Y$) losses in $\L_d$.
\btw{Sufficient condition for $\A$-normal convex integrand: $L$ is lower semi-continuous and $\mathcal{B}(\A) \otimes \Y$-measurable; $\E_p L(u,Y)$ finite for all $u, p$, there exists a $u_0$ for each $p$ so that $\E_p L(u_0, Y)$ is finite and continuous for Rockefellar's corollary, though it's stricter than Ioffe and Tokhimorov IIRC}
%Similarly, let $\L_d^{fin}$ be surrogates $L: \reals^d \times \Y \to \reals$ that are $\mathcal{B}(\reals^d) \otimes \Y$-measurable and minimizable, in the sense that $\argmin_{u} \exploss{L}{u}{p}$ is nonempty for all $p\in\P$-- we use this class of losses with finite $\Y$ in mind.
Set $\L = \cup_{d \in \mathbb{N}} \L_d$, and $\Lcvx = \cup_{d \in \mathbb{N}} \Lcvx_d$.
A loss $\ell: \R\times \Y \to \reals$ is \emph{discrete} if $\R$ is a finite set.
%A surrogate $L:\reals^d \times \Y \to \reals$ is \emph{convex} if $L(\cdot,y)$ is convex in $u$ almost surely in $\Y$.
For a given $p\in\P$, the (conditional) \emph{regret}, or excess risk, of a loss $L$ is given by $R_L(u,p) := \exploss{L}{u}{p} - \inf_{u^*} \exploss{L}{u^*}{p}$.
Typically, we notate finite report sets $\R$.

@@

\subsection{Property elicitation}\label{subsec:properties}
Arising from the statistics and economics literature, property elicitation is similar to calibration, but only characterizes exact minimizers of a surrogate~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting,lambert2009eliciting,lambert2018elicitation,frongillo2015vector-valued,frongillo2014general}.
Specifically, given a statistic or \emph{property} $\Gamma$ of interest, which maps a distribution $p \in \P \subseteq \simplex$ to the set of desired or correct predictions, the minimizers of $L$ should precisely coincide with $\Gamma$.
For intuition, to relate to consistency, one can think of $p = \Pr[Y|X=x]$ as a conditional distribution, though the definition is also applied to point prediction settings.

\begin{definition}[Property, elicits]
	A \emph{property} is a set-valued function $\Gamma : \P \to 2^\R \setminus \{\emptyset\}$, which we denote $\Gamma: \P \toto \R$.
	A loss $L : \R \times \Y \to \reals$ \emph{elicits} the property $\Gamma$ if
	\begin{equation}
    \label{eq:elic}    
    \forall p \in \P, \;\; \Gamma(p) = \argmin_{u \in \R} \exploss{L}{u}{p}~.
	\end{equation}
\end{definition}
An example is the mean, $\Gamma(p) = \{\E_p Y\}$.
The \emph{level set} of $\Gamma$ at value $r\in\R$ is $\Gamma_r := \{p \in \P : r \in \Gamma(p)\}$.
We call a property $\Gamma: \P \toto \R$ \emph{discrete} if $\R$ is a finite set, as in Quadrants 1 and 2.
A property is \emph{single-valued} if $|\Gamma(p)|=1$ for all $p\in\P$, in which case we may write $\Gamma:\P\to\R$ and $\Gamma(p) \in \R$.
The mean is single-valued.
We define the \emph{range} of a property by $\range \Gamma = \bigcup_{p\in\P} \Gamma(p) \subseteq \R$.
When $L\in\L$, we use $\Gamma := \prop[\P]{L}$ to denote the unique property elicited by $L$ (for distributions in $\P$) from eq.~\eqref{eq:elic}. 
Typically, we denote the target property by $\gamma$, and the surrogate by $\Gamma$.

@@

commenting out 01.25.2021 since we really just need one direction.
\begin{lemma}\label{lem:p-boundary-fsd}
	For any $p \in \P$ and $r$ such that $p \in \gamma_r$, take $\Y' := \supp(p)$.
	Define $\gamma' : \P \toto \R$ with $\gamma' : q \mapsto \gamma(q) \cap \simplexp$.
	Then $\Sc_{\gamma_r}(p) = \Sc_{\gamma'_r}(p)$.
\end{lemma}
\begin{proof}
	Consider the ambient space of both $\Sc_{\gamma_r}(p)$ and $\Sc_{\gamma'_r}(p)$ is $\reals^\Y$.
	We trivially have $\dim(\Sc_{\gamma_r}(p)) \geq \dim(\Sc_{\gamma'_r}(p))$ since $\gamma'$ is simply $\gamma$ projected down to an affine subspace of $\reals^\Y$.

@@

  \raf{Show that $L'$ indirectly elicits $\gamma'$.}
  By consistency, we have $L$ indirectly eliciting $\gamma$.
  Now, observe $L'$ (eliciting $\Gamma'$) indirectly elicits $\gamma' := \prop[\simplexp]{\ell'}$ since, for all $q \in \simplex$, taking $B : q \mapsto \{q_{y} \mid y > 0\}$, and in particular, $p' = B(p)$, we have $p' \in \Gamma'_u \implies p' \in \gamma'_{\psi(u)}$.
  Moreover, $\Gamma(p) = \Gamma'(p')$ and $\gamma(p) = \gamma'(p')$.
  This same observation can be used to observe that $L'$ is also calibrated with respect to $\ell'$ as the calibration bound holds for all $q \in \simplex$, and .

  \raf{Show $\dim(\Sc_{\gamma_r}(p)) \geq \dim(\Sc_{\gamma'_r}(p'))$}
  Moreover, we have $\Sc_{\gamma_r}(p) \supseteq \Sc_{\gamma'_r}(p')$...

>>>>

If given, we use $\ell: \R \times \Y \to \reals$ to denote a \emph{target loss}, with predictions $r\in\R$.
%where the goal is minimize expected loss, $\E ~ \ell(f(X),Y)$ for pairs $X,Y$ drawn from some distribution.
Similarly, $L: \reals^d \times \Y \to \reals$ will typically denote a \emph{surrogate} loss, with surrogate predictions $u \in \reals^d$.
We write $\L_d $ for the set of $\mathcal{B}(\reals^d) \otimes \Y$-measurable and lower semi-continuous surrogates $L : \reals^d \times\Y \to \reals$ such that $\E_{Y \sim p} L(u,Y) < \infty$ for all $u \in \reals^d, p \in \P$, and are minimizable, in the sense that $\argmin_{u} \exploss{L}{u}{p}$ is nonempty for all $p\in\P$.
Moreover, $\Lcvx_d \subseteq \L_d$ is the set of convex (in $\reals^d$ for every $y \in \Y$) losses in $\L_d$.
\btw{Sufficient condition for $\A$-normal convex integrand: $L$ is lower semi-continuous and $\mathcal{B}(\A) \otimes \Y$-measurable; $\E_p L(u,Y)$ finite for all $u, p$, there exists a $u_0$ for each $p$ so that $\E_p L(u_0, Y)$ is finite and continuous for Rockefellar's corollary, though it's stricter than Ioffe and Tokhimorov IIRC}
%Similarly, let $\L_d^{fin}$ be surrogates $L: \reals^d \times \Y \to \reals$ that are $\mathcal{B}(\reals^d) \otimes \Y$-measurable and minimizable, in the sense that $\argmin_{u} \exploss{L}{u}{p}$ is nonempty for all $p\in\P$-- we use this class of losses with finite $\Y$ in mind.
Set $\L = \cup_{d \in \mathbb{N}} \L_d$, and $\Lcvx = \cup_{d \in \mathbb{N}} \Lcvx_d$.
A loss $\ell: \R\times \Y \to \reals$ is \emph{discrete} if $\R$ is a finite set.
%A surrogate $L:\reals^d \times \Y \to \reals$ is \emph{convex} if $L(\cdot,y)$ is convex in $u$ almost surely in $\Y$.
For a given $p\in\P$, the (conditional) \emph{regret}, or excess risk, of a loss $L$ is given by $R_L(u,p) := \exploss{L}{u}{p} - \inf_{u^*} \exploss{L}{u^*}{p}$.
Typically, we notate finite report sets $\R$.

@@

\subsection{Property elicitation}\label{subsec:properties}
Arising from the statistics and economics literature, property elicitation is similar to calibration, but only characterizes exact minimizers of a surrogate~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting,lambert2009eliciting,lambert2018elicitation,frongillo2015vector-valued,frongillo2014general}.
Specifically, given a statistic or \emph{property} $\Gamma$ of interest, which maps a distribution $p \in \P \subseteq \simplex$ to the set of desired or correct predictions, the minimizers of $L$ should precisely coincide with $\Gamma$.
\bo{Should give at least one example? Squared loss?}
For intuition, to relate to consistency, one can think of $p = \Pr[Y|X=x]$ as a conditional distribution, though the definition is also applied to point prediction settings.

\begin{definition}[Property, elicits]
	A \emph{property} is a set-valued function $\Gamma : \P \to 2^\R \setminus \{\emptyset\}$, which we denote $\Gamma: \P \toto \R$.
	A loss $L : \R \times \Y \to \reals$ \emph{elicits} the property $\Gamma$ if
	\begin{equation}
    \label{eq:elic}    
    \forall p \in \P, \;\; \Gamma(p) = \argmin_{u \in \R} \exploss{L}{u}{p}~.
	\end{equation}
\end{definition}

The \emph{level set} of $\Gamma$ at value $r\in\R$ is $\Gamma_r := \{p \in \P : r \in \Gamma(p)\}$.
We call a property $\Gamma: \P \toto \R$ \emph{discrete} if $\R$ is a finite set, as in Quadrants 1 and 2.
A property is \emph{single-valued} if $|\Gamma(p)|=1$ for all $p\in\P$, in which case we may write $\Gamma:\P\to\R$ and $\Gamma(p) \in \R$.
We define the \emph{range} of a property by $\range \Gamma = \bigcup_{p\in\P} \Gamma(p) \subseteq \R$.
When $L\in\L$, we use $\Gamma := \prop[\P]{L}$ to denote the unique property elicited by $L$ (for distributions in $\P$) from eq.~\eqref{eq:elic}. 
Typically, we denote the target property by $\gamma$, and the surrogate by $\Gamma$.

@@

%commenting out 01.25.2021 since we really just need one direction.
\begin{lemma}\label{lem:p-boundary-fsd}
	For any $p \in \P$ and $r$ such that $p \in \gamma_r$, take $\Y' := \supp(p)$.
	Define $\gamma' : \P \toto \R$ with $\gamma' : q \mapsto \gamma(q) \cap \simplexp$.
	Then $\Sc_{\gamma_r}(p) = \Sc_{\gamma'_r}(p)$.
\end{lemma}
\begin{proof}
	Consider the ambient space of both $\Sc_{\gamma_r}(p)$ and $\Sc_{\gamma'_r}(p)$ is $\reals^\Y$.
	We trivially have $\dim(\Sc_{\gamma_r}(p)) \geq \dim(\Sc_{\gamma'_r}(p))$ since $\gamma'$ is simply $\gamma$ projected down to an affine subspace of $\reals^\Y$.

@@

  \raf{Show that $L'$ indirectly elicits $\gamma'$.}
  We wish to first  show $L'$ indirectly elicits $\gamma'$.
  Since $L$ indirectly elicits $\gamma$, we have a link $\psi$ such that for all $u \in \reals^d$, $\Gamma_u \subseteq \gamma_{\psi(u)}$.
  As $\Gamma'(q) = \Gamma(h(q))$ and $\gamma'(q) = \gamma(h(q))$\jessiet{Hand waving}, we have $q \in \Gamma'_u \iff h(q) \in \Gamma_u \implies h(q) \in \gamma_{\psi(u)} \iff (q_y)_{y \in \Y'} \in \gamma'_{\psi(u)}$, and therefore, $L'$ indirectly elicits $\gamma'$ via the link $\psi \circ \proj(\Y')$, where $\proj(\Y') : q \mapsto (q_y)_{y \in \Y'}$. 
%  By consistency, we have $L$ indirectly eliciting $\gamma$.
%  Now, observe $L'$ (eliciting $\Gamma'$) indirectly elicits $\gamma' := \prop[\simplexp]{\ell'}$ since, for all $q \in \simplex$, taking $B : q \mapsto \{q_{y} \mid y > 0\}$, and in particular, $p' = B(p)$, we have $p' \in \Gamma'_u \implies p' \in \gamma'_{\psi(u)}$.
%  Moreover, $\Gamma(p) = \Gamma'(p')$ and $\gamma(p) = \gamma'(p')$.
%  This same observation can be used to observe that $L'$ is also calibrated with respect to $\ell'$ as the calibration bound holds for all $q \in \simplex$, and .

  \raf{Show $\dim(\Sc_{\gamma_r}(p)) \geq \dim(\Sc_{\gamma'_r}(p'))$}
  Let $\{v_i\}_{i=1}^k$ form a basis for $\Sc_{\gamma_r}(p))$.
  If there is some $v' \in \Sc_{\gamma'_r}(p')$ that cannot be written as $\sum_{i=1}^k \alpha_i v_i$, then we claim $\{v_i\}_{i=1}^k$ does not form a basis for $\Sc_{\gamma_r}(p))$.
  In particular, consider $q := h(v' + p')$; we have $q \in \gamma_r$, and $q - p \in \Sc_{\gamma_r}(p)$.
  However, as $v'$ cannot be written $\sum_{i=1}^k \alpha_i v_i$, neither can $q$, so we have $\{v_i\}_{i=1}^k$ is not a basis for $\Sc_{\gamma_r}(p)$.\jessiet{So much hand waving}
  Thus, we have $\dim(\Sc_{\gamma_r}(p)) \geq \dim(\Sc_{\gamma'_r}(p'))$.

%  Consider $\gamma_r = h(\gamma'_r) = \{h(q') \mid q' \in \gamma'_r\}$.
%  Then $v \in \Sc_{\gamma_r}(h(p')) \implies \exists \epsilon_0$ so that $h(p') + \epsilon v \in \gamma_r \forall \epsilon \in (-\epsilon_0, \epsilon_0)$ if and only if $p' + \epsilon v \in \gamma'_r \forall \epsilon \in (-\epsilon_0, \epsilon_0)$.
%  Moreover, we have $\Sc_{\gamma_r}(p) \supseteq \Sc_{\gamma'_r}(p')$...
